An Empirical Analysis of C Preprocessor Use

### 2000-01-18 macros/papers/emp-use-2.tex
Added missing exact number re: perl anomaly w.r.t unknown identifier macro defs.
OK, I added *one single sentence* at the very, very end of the paper. Kind of wimpy, but maybe OK.

  In \pkg{perl}, unknown identifiers make up 31\% of macro definitions,
  compared to an average of 6.9\% and \verb|ABOUT 9% NEED EXACT NUMBER| in
  \pkg{mosaic}, which has the the second largest proportion of unknown
  identifiers.  In order to avoid link-time collisions when the Perl
  interpreter is embedded in another application, \pkg{perl} conditionally
  redefines over one thousand global symbols to add the prefix
  \verb|Perl_|, as in {\tt \#define Xpv Perl_Xpv}.

@@

Finally, our results are of interest to software engineers researchers
for all of the above reasons and more.  Since this is the first study
of Cpp usage of which we are aware, it was worth performing simply to
determine whether the results were predictable \emph{a priori}; in
addition, we found some interesting, and in some cases surprising,
features of our suite of programs.

>>>>

  In \pkg{perl}, unknown identifiers make up 31\% of macro definitions,
  compared to an average of 6.9\% and 9.0\% in
  \pkg{mosaic}, which has the the second largest proportion of unknown
  identifiers.  In order to avoid link-time collisions when the Perl
  interpreter is embedded in another application, \pkg{perl} conditionally
  redefines over one thousand global symbols to add the prefix
  \verb|Perl_|, as in {\tt \#define Xpv Perl_Xpv}.

@@

Finally, our results are of interest to software engineers researchers
for all of the above reasons and more.  Since this is the first study
of Cpp usage of which we are aware, it was worth performing simply to
determine whether the results were predictable \emph{a priori}; in
addition, we found some interesting, and in some cases surprising,
features of our suite of programs.  More highly focused and deeper analyses
would be worthwhile.
